### 2012-01-10 paper.tex
Adjusted to literature.bib
Added some very preliminary content and an extra reference

\section{Introduction}

\section{Experimental Methods}
The measurents are done in a silicon-fabricated microreactor, developed here at CINF (REF!)....

\section{Results}
Several different samples deposited at various diffent sizes and amounts all show the oscillating bahaviour. Repeatability is high regarding running long experiments on a single sample, but very low from sample to sample.

\section{Discussion}
....

@@

\footnotesize{
\bibliography{rsc} %your .bib file
\bibliographystyle{rsc} %the RSC's .bst file
}

>>>>

\section{Introduction}
Oxidation of CO is a classic model system for testing catalytic properties of various materials. It was shown already in 1985 (REF) that this reaction will show oscilaltory behaviour under UHV conditions due to surface reconstructions having large influence on the catalytic activity of the surface. However, this is a phenomenon that is only observed under UHV-condition, under higher pressures these kinds of reconstructions will happen. In this paper we show sustained catalytic oscilations on Platinum nano particles that due to their sometimes extremely long time-scales cannot be a surface phenomenon, but must involve a bulk oxidation of the nanoparticle.

\section{Experimental Methods}
The measurents are done in a silicon-fabricated microreactor, developed here at CINF \cite{Henriksen2009}. The reactor consists of a two inlets, a long mixing zone for the incoming gases and a reactor of total volume of $240\,$nL. The reactor is able to operate at a pressure range og 0-2.5\,bar. The gases is supplied through ordinary flow controllers capable of controlling flow in the range of a few mL/min. The flow is reduced to a value capable of being fed into a mass-spectrometer by passing most of the flow through an outlet connected to a pressure controller. A small part of the flow is led into the reactor chamber and via a $5.4\,\mu$m wide capillary further into UHV chamber equiped with a quadropole mass spectrometer. The design ensures that all gas exposed to the catalyst under investigation is also measured in the mass spectrometer ensures a very high sensitivity of the device. When an evacuated microreactor is mounted, the base pressure of the UHV chambe is $\sim5\times10^{-9}\,$mbar and when operating at $1\,$bar in the reactor the pressure is $\sim5\times10^{-7}\,$mbar.

The reactor is heated by a Pt heating element evaporated on the backside that at the same time acts as an RTD to measure the temperature.

\section{Sample preparation}
The samples was made by depositing a very small amount of size-selcted clusters from a quadropole cluster source (REF!) onto the microreactores. Typical sizes are in the order of 3-9\,nm and the coverage is kept at approximately 0.1\% geometric coverage, found by measuring the current from the charged clusters landing on the reactor. After deposition the reactor is anonicly bonded to a pyrex lid while keeping the reactor area cold by mounting the reactor on a cooling block and heating the rest of the sample to $\sim350\,^\circ$C \cite{Vesborg2010}

\section{Results}
The experiments was carried out 
Several different samples deposited at various diffent sizes and amounts all show the oscillating bahaviour. Repeatability is high regarding running long experiments on a single sample, but very low from sample to sample.

\section{Discussion}
Due to long timescales involved which are much larger than any typically orcurring timescales for such a small system, there can be little doubt that this phenomenon involves some kind of reaction involving the bulk of the nano particles.

@@

\footnotesize{
\bibliography{literature} %your .bib file
\bibliographystyle{rsc} %the RSC's .bst file
}
